Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-09 paper/paper.qmd
Updated survey objectives and a bit of sampling approaching in appendix

### Idealized Survey Objectives
The objective of our survey is to obtain information about the investigators from US police departments and their experience with dealing with homicide cases. This information would be used to take into account any potential factors about police officers that could potentially impact if a homicide case ends up unsolved. Currently, we only have state collected homicide data that is collected by the FBI with basic demographic, temporal, and geographic information. @citeJohnson looked at prison data and noted that the standards in place with state collected data do not help us fully understand the cause and impact of the US prison system. This can also be applied to homicide data where we can not say we fully understand the cause of homicide cases going unsolved. Thus, this led us to conducting this survey to further understand the crime case system better and what interventions may be needed, which is also noted by @citeJohnson when collecting community sourced prison data. In the following idealized methodology, we will cover our sampling approach and respondent recruitment, data validation, the design of our survey, limitations of our survey, a link to how the survey could look, and the survey questions themselves.

@@

Our target population are all investigators from US police departments as defined by [@citetellingstories]. However, since we can not survey every investigator in the US, we will narrow down our group to be investigators from 5 US police department across the United States like the Chicago Police department who are responsible for homicide cases and located in large cities, which is our sampling frame. More specifically, our sample will be all the investigators from 5 US police department in large cities such as the Chicago Police Department who are responsible for homicide cases and who we can gather data on [@citetellingstories].

>>>>

### Idealized Survey Objectives
The objective of our survey is to obtain information about the investigators from US police departments and their experience with dealing with homicide cases. This information would be used to take into account any potential factors about police officers that could potentially impact if a homicide case ends up unsolved. Currently, we only have state collected homicide data that is collected by the FBI with basic demographic, temporal, and geographic information. @citeJohnson looked at prison data and noted that the standards in place with state collected data do not help us fully understand the cause and impact of the US prison system. The data collected often only looked at the individuals in prison and not considered structural factors like the public's opinion to crime policies [@citeJohnson]. This can also be applied to homicide data where we can not say we fully understand the cause of homicide cases going unsolved by only looking at the victim's characteristics and where they were found. Thus, this led us to conducting this survey to further understand the crime case system better and what interventions may be needed, which is also noted by @citeJohnson on community sourced prison data. Community source data involves obtaining data from the people living in or with the system itself, as defined by @citeJohnson, and in our case, our survey aims to collect data from people who maintain the homicide case system. In the following idealized methodology, we will cover our sampling approach and respondent recruitment, data validation, the design of our survey, limitations of our survey, a link to how the survey could look, and the survey questions themselves.

@@

Our target population are all investigators from US police departments as defined by [@citetellingstories]. However, since we can not survey every investigator in the US, we will narrow down our group to be investigators from 5 US police department across the United States who are responsible for homicide cases and are located in large cities, which is our sampling frame. More specifically, our sample will be all the investigators from 5 US police department in large cities who are responsible for homicide cases and who we can gather data on [@citetellingstories].
